Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2019-10-19 manuscript/manuscript.tex
updated ms

\Section{Materials and Methods}

@@

\subsection{Estimating $G(t)$ and the Convergence Correlation}

\subsection{Block Bootstrap}

@@

@@

To infer the uncertainty of covariance, convergence correlation, and $G(t)$
estimates, we used a block bootstrap procedure. This is a version of the
bootstrap that resamples blocks of data points, rather than individual data
points, to infer the uncertainty of an statistic in the presence of unknown
correlation structure between data. With genome-wide data, linkage
disequilibria between sites creates complex and unknown dependencies between
variants. The estimators used in this paper are predominantly ratios, e.g.
temporal-replicate covariance standardized by half the heterozygosity, $G(t)$
which is the ratio of covariance to total variance, and the convergence
correlation (equation \eqref{eq:conv-corr}). In these cases, we can exploit the
linearity of the expectation to make the bootstrap procedure more
computationally efficient, by pre-calculating the statistics of the ratio's
numerator and denominator, $N(\mathbf{x}_i)$ and $D(\mathbf{x}_i)$, on the data
$\mathbf{x}_i$ for all blocks $i \in \{1, 2, \ldots, W\}$ in the genome. Then
we draw $W$ bootstrap samples with replacement, and compute the estimate for
bootstrap sample $b$ with an average weighted by the fraction $w_i$ of total
loci contained in each block,

@@

@@

  \label{suppfig:barghi-tailprobs-seqid}
\end{figure}
\end{document}

>>>>

\section{Materials and Methods}

@@

\subsection{Estimating Uncertainty with a Block Bootstrap}

To infer the uncertainty of covariance, convergence correlation, and $G(t)$
estimates, we used a block bootstrap procedure. This bootstrap procedure
resamples blocks of data points, rather than individual data points, to infer
the uncertainty of an statistic in the presence of unknown correlation between
loci. As most estimators in this paper are ratios (e.g. covariance standardize
by sample heterozygosity, $G(t)$, and the convergence correlation) which we
estimate with a ratio of averages, we exploit the linearity of expectation for
efficient computation of bootstrap samples (see \ref{supp:block-bootstrap} for
details).

@@

\subsection{Windowed Covariance and the Empirical Neutral Null}

@@

The estimators used in this paper are predominantly ratios, e.g.
temporal-replicate covariance standardized by half the heterozygosity, $G(t)$
which is the ratio of covariance to total variance, and the convergence
correlation (equation \eqref{eq:conv-corr}). In these cases, we can exploit the
linearity of the expectation to make the bootstrap procedure more
computationally efficient, by pre-calculating the statistics of the ratio's
numerator and denominator, $N(\mathbf{x}_i)$ and $D(\mathbf{x}_i)$, on the data
$\mathbf{x}_i$ for all blocks $i \in \{1, 2, \ldots, W\}$ in the genome. Then
we draw $W$ bootstrap samples with replacement, and compute the estimate for
bootstrap sample $b$ with an average weighted by the fraction $w_i$ of total
loci contained in each block,

@@

\subsection{PCA of \textcite{Barghi2019-qy} replicates}

  \includegraphics[]{figures/barghi-panel-pca.pdf}

  \caption{A PCA on the centered and standardized population frequencies for
  each replicate (each color) for all its sequenced timepoints (the connected
  series of points). All replicates start from the same source population, and
  thus are overlapping in the center; as each replicate evolves independently it
  diverges from the other replicates in PCA space.}

  \label{suppfig:barghi-pca}
\end{figure}

@@

  \label{suppfig:barghi-tailprobs-seqid}
\end{figure}

\end{document}
